---
title: "Alcohol vs Seat choice"
author: "Tom Weadock"
date: "Spring 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

From looking at the box plot, since the boxes overlap, there appears to be no significant difference between alcohol consumption and row.  Also, from the notched box plot, the standard deviation of alcohol consumption in the back row looks to be much higher than in the other rows.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The numerical summary confirms the difference in standard deviation.  In addition, although Q3 is much higher in the back row, and the mean is much higher in the back row, we still see that Q1 to Q3 overlap between the rows.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The probability from the one-way Anova test is low.  Therefore, we reject the null hypothesis, and there is a significant difference among the groups.  A further test must be performed to identify the specific differences.


```{r}
plot(TukeyHSD(model1))
```

The Tukey test identified that there is no significant difference between the middle and front groups because the 95% confidence interval contains the value of 0.  However, because the 95% CI are all on one side of zero, there is a signficant difference for alcohol consumed between the middle and back groups and between the front and back groups.

## Conclusions

From the initial boxplot and numerical summary, there did not appear to be a significant difference.  However, the one-way Anova test revealed differences between the groups by a low p-value.  The Tukey test was used to perform t-tests between the individual groups and significant differences between the middle and back groups and between the front and back groups were shown.
